Towards Comparable Active Learning

### 2023-05-12 doc/al_benchmark_paper.tex
lstm model _encode function

\documentclass[]{article}
\usepackage[a4paper, total={6.5in, 8.5in}]{geometry}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}

\title{Towards Comparable Active Learning}

@@

@@

\subsection{Contribution}

@@

\section{Comparison of different sample sizes $\tau$}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\linewidth]{img/tau_ablation.png}
\end{figure}

>>>>

\documentclass[]{article}
%\usepackage[a4paper, total={6.5in, 8.5in}]{geometry}
\usepackage{color}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{neurips_data_2023}

\title{Towards Comparable Active Learning}
\author{%
	David S.~Hippocampus\thanks{Use footnote for providing further information
		about author (webpage, alternative address)---\emph{not} for acknowledging
		funding agencies.} \\
	Department of Computer Science\\
	Cranberry-Lemon University\\
	Pittsburgh, PA 15213 \\
	\texttt{hippo@cs.cranberry-lemon.edu} \\
	% examples of more authors
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \AND
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
}

@@

\begin{abstract}
	The abstract paragraph should be indented $\frac{1}{2}$~inch (3~picas) on
	both the left- and right-hand margins. Use 10~point type, with a vertical
	spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
	bold, and in point size 12. Two line spaces precede the abstract. The abstract
	must be limited to one paragraph.
\end{abstract}

@@

\subsection{Contributions}
\begin{enumerate}
	\item Evaluation of Active Learning algorithms on datasets from 4 different domains, including synthetic data that highlights principled shortcomings of existing approaches.
	\item Novel experimental protocol for seeding the experiment with 3 different seeds to allow full control and reproducibility and analysis of how many restarts are required to converge to the true median performance reliably.
	\item Simple algorithm for an Oracle-Curve that can be constructed greedily and does not rely on search.
\end{enumerate}

@@

\section{Comparison of different sample sizes}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\linewidth]{img/tau_ablation.png}
\end{figure}
